Inferring Continuous and Discrete Population Genetic Structure Across Space

### 2017-09-13 writeup/cover_letter.tex
tweaked cover letter

Submission Cover Letter\\
\emph{PLoS Biology}
\\\\\\
To the Editor(s),

@@

As of this submission, \texttt{STRUCTURE} alone has been cited more than 20,000 times, 
and the falling costs of sequencing are facilitating an explosion of next-generation sequence datasets.  
The first step in the analysis of these data will, for most researchers, 
involve a model-based clustering analysis.
We therefore believe that our work represents an important and timely contribution to the field.

>>>>

Submission Cover Letter \hfill	\today\\
\emph{PLoS Biology}
\\\\\\
To the Editor(s),

@@

As of this submission, \texttt{STRUCTURE} alone has been cited more than 20,000 times, 
and the ever-falling costs of sequencing are facilitating an explosion of next-generation sequence datasets.  
The first step in the analysis of these data will, for most researchers, 
involve a model-based clustering analysis.
We therefore believe that our work represents an important and timely contribution to the field.
